# 2. Regression and model validation

The dataset used in this exercise includes performance, age and gender of students combined with a questionnaire about attitude, surface thinking, strategic thinking and deep thinking.

[This](http://www.helsinki.fi/~kvehkala/JYTmooc/JYTOPKYS3-meta.txt) link will include more information about the original dataset.

```{r, echo=FALSE}
setwd("C:/R_work/GIT/IODS-project/IODS-project")
students2014<-read.table(file= "learning2014.csv")
```
The dataset structure and dimensions are the following:
```{r, echo=TRUE}
str(students2014)
dim(students2014)
```





*Describe the work you have done this week and summarize your learning.*
Dataset was prepared

- Describe your work and results clearly. 
- Assume the reader has an introductory course level understanding of writing and reading R code as well as statistical methods
- Assume the reader has no previous knowledge of your data or the more advanced methods you are using  



Read the students2014 data into R either from your local folder (if you completed the Data wrangling part) or from this url: http://s3.amazonaws.com/assets.datacamp.com/production/course_2218/datasets/learning2014.txt . (The separator is a comma "," and the file includes a header). Explore the structure and the dimensions of the data and describe the dataset briefly, assuming the reader has no previous knowledge of it. There is information related to the data here. (0-2 points)