# 2. Regression and model validation

## 2.1 Dataset
The dataset used in this exercise includes exam points, age and gender of students combined with a questionnaire about attitude, surface thinking, strategic thinking and deep thinking.

[This](http://www.helsinki.fi/~kvehkala/JYTmooc/JYTOPKYS3-meta.txt) link will include more information about the original dataset.

```{r, echo=FALSE}
setwd("C:/R_work/GIT/IODS-project/IODS-project")
students2014<-read.table(file= "learning2014.csv")
```
The dataset structure and dimensions are the following:
```{r, echo=TRUE}
str(students2014)
dim(students2014)
```
Questions from different categories we combined into means for each student. Students with 0 points were left out.

## 2.2 Graphical overview


```{r, echo=FALSE, include=FALSE}
library(GGally)
library(ggplot2)
```
Scatter plot matrix of the dataset broken down by gender.
```{r, echo=FALSE}

p <- ggpairs(students2014, mapping = aes(col = gender, alpha = 0.3), lower = list(combo = wrap("facethist", bins = 20)))
p

```
  
Summaries of each column of the dataset:
```{r, echo=TRUE}

summary(students2014$gender)
summary(students2014$Age)
summary(students2014$Attitude)
summary(students2014$deep)
summary(students2014$stra)
summary(students2014$surf)
summary(students2014$Points)

```
Findings:

* From the plot it can be seen that the strongest correlation can be found between Attitude and Points.
* Majority of the students are in the twenties. Older students increase the age mean heavily compared to median.

## 2.3 Model









*Describe the work you have done this week and summarize your learning.*

Read the students2014 data into R either from your local folder (if you completed the Data wrangling part) or from this url: http://s3.amazonaws.com/assets.datacamp.com/production/course_2218/datasets/learning2014.txt . (The separator is a comma "," and the file includes a header). Explore the structure and the dimensions of the data and describe the dataset briefly, assuming the reader has no previous knowledge of it. There is information related to the data here. (0-2 points)